\section{Results from Prior Support}

\noindent \textbf{Dr. Britton Smith:} Dr. Smith is a Co-PI on one
NSF-funded project, NSF AST-1615848 ``Collaborative Research: CDS\&E:
Renaissance Simulations Laboratory to Model and Explore the First
Galaxies in the Universe'' (PI Michael
Norman; \$440k).  \textbf{Intellectual merits:} The purpose of this
grant is to enable further analysis of the Renaissance
Simulations \citep{2015ApJ...807L..12O} and to create an open-access
data analysis portal, known as the ``Renaissance Simulation
Laboratory'' (RSL), to provide the astronomical community with access
to the raw data, analysis data products, and tools of the Renaissance
Simulations.  The RSL provides a data analysis workflow that allows users to
run custom analysis on any of the hosted data and to download and/or
share their data products and scripts.  \textbf{Broader impacts:}
This awards aims to provide open access to this set of cutting-edge
simulations and associate tools to the entire astronomical community,
independent of a user's local computing resources.  This both
increases the return on investment in the simulations and helps to
level the playing field for scientific research with large data sets.
Protypes for the RSL's tutorial, Jupyter notebook environment, and
relational database for halo catalogs are up
at \url{https://rensimlab.github.io/}, \url{https://girder.rensimlab.xyz/}, 
and \url{https://galaxyportal.sdsc.edu/}.
Publications: \citep{2016ApJ...832L...5X, 2016ApJ...833...84X,
Barrow17_FL2, 2017ApJ...845...47T, 2017ApJ...847...59H}.

\mjt{Matt, your grants here!}
